Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms.tex
shorten abstract

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, IR luminosity, and
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
than the local value
but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXS\,J1131$-$1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\subsection{The $M_{\rm BH}$$-$\mbulge Relation}
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\%
using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
and the stellar mass derived in \Sec{SED} as an upper limit to the bulge mass.
This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
but is higher than those of nearby AGNs \citep{HR04a}, supporting
the emerging picture that quasars
grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a,Riechers08a}.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
suggests that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\subsection{The $M_{\rm BH}$$-$\mbulge Relation}
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\%
using the black hole mass of $M_{\rm BH}$\ssim8\E{7}\,\Msun \citep{Sluse12a}
and the stellar mass derived in \Sec{SED} as an upper limit to the bulge mass.
This ratio is consistent with those of other intermediate-$z$ radio-loud AGNs \citep{McLure06a}
but is higher than those of nearby AGNs \citep{HR04a}, supporting
the emerging picture that quasars
grow faster and/or earlier than their host galaxies at higher redshifts \citep[e.g., ][]{Walter04a, Peng06a, McLure06a,Riechers08a}.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of RXJ1131 compared to local AGNs
suggests that the bulk of the black hole mass of RXJ1131 is largely in place while its stellar bulge is still assembling.
